A framework for mentored data science research

### 2019-12-14 Rmd/methods.Rmd
added submission materials.

In planning with students for poster and slide presentations, 
we (Hanlon and Boehm) emphasized
the importance of succinctly stating the research question and its scientific 
context. After clarifying the importance of the question, the student could 
proceed with explaining many of the elements that we've described above. Namely, the 
student would discuss the analyzed data and its acquisition while noting any shortcomings or 
biases of the data. For oral presentations, we suggested that 
students cautiously limit discussion of statistical methods, with the caveat that 
they prepare to answer detailed methodological inquiries during the question and 
answer session. 
Our students created powerful data 
visualizations for their projects. Their presentations also included their major results and future research directions.

>>>>

In planning with students for poster and slide presentations, 
we emphasized
the importance of succinctly stating the research question and its scientific 
context. After clarifying the importance of the question, the student could 
proceed with explaining many of the elements that we've described above. Namely, the 
student would discuss the analyzed data and its acquisition while noting any shortcomings or 
biases of the data. For oral presentations, we suggested that 
students cautiously limit discussion of statistical methods, with the caveat that 
they prepare to answer detailed methodological inquiries during the question and 
answer session. 
Our students created powerful data 
visualizations for their projects. Their presentations also included their major results and future research directions.
